Multi-channel Kondo model URG

### 2021-12-10 notes/multi-channel-urg.tex
started writing spin-S impurity Kondo URG

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
\usepackage[hidelinks]{hyperref}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\tableofcontents
\section{Introduction of the Hamiltonian and its zero mode}
The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
\begin{align}
	\label{mc_ham}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{align}
In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The presence of a common spin-exchange coupling \(J\) for all the channels is what makes the problem isotropic with respect to the channels.

@@

\section{Eigenvalues and eigenstates}
The star graph can be diagonalized. Since the Hamiltonian commutes with \(s_\text{tot}^2\), it is already block-diagonal in the quantum number \(s_\text{tot}\). Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\). For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \). The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\). From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\). So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\). We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on whether it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks. To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)). The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \). The fact that this block does not interact with the other blocks can be easily verified: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down. This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.

@@

\section{Importance of the star graph}
Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}. Instead, the RG flows converge to an intermediate coupling fixed point. The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}. For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow. Analytic and numerical studies also showed that \textit{the two and three-channel models enjoy a weak-strong duality}~\cite{kroha_kolf_2007,zitko_fabrizio_2017}: the model at strong coupling, when projected onto the ground state basis, can also be thought of as a Kondo model at weak coupling, but possibly with a modified central spin. For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}. The strong and weak coupling models are formally identical and the model is self-dual. The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state. Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-1/2 and a spin-1 model. We will now show that these qualitative features can be captured very simply by the star graph.

@@

\clearpage
\appendix
\section{URG analysis of the single-channel Kondo model}
The single-channel SU(2) Kondo model consists of a spin-half impurity interacting with a band of itinerant conduction electrons through a spin-exchange coupling:
\label{1KondoURG}
\begin{align}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
\end{align}
Here, \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\). Also, \(\tau = \hat n - \frac{1}{2}\). The indices \(k,l\) sum over the momentum states. \(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm 1/2\).

@@

>>>>

\documentclass[12pt]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
\usepackage[hidelinks]{hyperref}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\tableofcontents
\section{Introduction of the Hamiltonian and its zero mode}
The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
\begin{align}
	\label{mc_ham}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{align}
In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The presence of a common spin-exchange coupling \(J\) for all the channels is what makes the problem isotropic with respect to the channels.

@@

\section{Eigenvalues and eigenstates of the star graph}
The star graph can be diagonalized. Since the Hamiltonian commutes with \(s_\text{tot}^2\), it is already block-diagonal in the quantum number \(s_\text{tot}\). Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\). For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \). The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\). From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\). So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\). We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on whether it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks. To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)). The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \). The fact that this block does not interact with the other blocks can be easily verified: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down. This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.

@@

\section{Importance of the star graph in determining the physics of the problem}
Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}. Instead, the RG flows converge to an intermediate coupling fixed point. The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}. For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow. Analytic and numerical studies also showed that \textit{the two and three-channel models enjoy a weak-strong duality}~\cite{kroha_kolf_2007,zitko_fabrizio_2017}: the model at strong coupling, when projected onto the ground state basis, can also be thought of as a Kondo model at weak coupling, but possibly with a modified central spin. For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}. The strong and weak coupling models are formally identical and the model is self-dual. The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state. Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-1/2 and a spin-1 model. We will now show that these qualitative features can be captured very simply by the star graph.

@@

\clearpage
\appendix
\section{URG equations for the single-channel Kondo model}
The single-channel SU(2) Kondo model consists of a spin-half impurity interacting with a band of itinerant conduction electrons through a spin-exchange coupling:
\begin{align}
\label{1KondoURG}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
\end{align}
Here, \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\). Also, \(\tau = \hat n - \frac{1}{2}\). The indices \(k,l\) sum over the momentum states. \(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm 1/2\).

@@

\section{URG equations for the single-channel Kondo model with spin-\(S\) impurity}
The Hamiltonian is the same as eq.~\ref{1KondoURG}, but the impurity is now a spin-\(S\) object, such that \(S_d^z \in \left[-S, -S+1,\ldots,S-1,S\right] \). We will also choose different couplings \(J_m\) for each of the eigenvalues of \(S_d^z\):
\begin{equation}\begin{aligned}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k}\sum_{m=-S}^S J^z_m S_d^z s^z_{k}\ket{m}\bra{m} + \frac{1}{2}\sum_{k}\sum_{m=-S}^S J^t_m \left(S_d^+ s^-_{k} \ket{m}\bra{m} + \text{h.c.}\right)
\end{aligned}\end{equation}
The states \(\ket{m}\) act purely on the Hilbert space of the impurity spin and are defined as \(S_d^z\ket{m} = m\ket{m}\). We will use the relations:
\begin{equation}\begin{aligned}
	S_d^\pm S_d^z &= S_d^z S_d^\pm \mp S_d^\pm\\
	S_d^z S_d^\pm &= S_d^\pm S_d^z \pm S_d^\pm\\
	S_d^\pm S_d^\mp &= \vec S_d^2 - {S_d^z}^2 \pm S_d^z
\end{aligned}\end{equation}
The various terms that renormalize the Hamiltonian can be described in terms of the impurity spin operators that come into them. For example, the term that has \(S_d^z\) on both sides of the intervening Greens function can be represented as \(z-z\). There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\). Each of these terms occur both in the particle and the hole sectors.
\subsection{Particle sector}
We will now calculate each of these terms for the particle sector. The particle sector consists of those processes that start from an occupied state \(\hat n_{q\beta} = 1\).
\paragraph{\(z|z: \beta=\uparrow\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m}^2 c^\dagger_{q \uparrow} c_{k^\prime \uparrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^z c^\dagger_{k \uparrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^z_m}^2{S_d^z}^2 c^\dagger_{k \uparrow}c_{k^\prime\uparrow} \ket{m}\bra{m}}{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(z|z: \beta=\downarrow\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m}^2 c^\dagger_{q \downarrow} c_{k^\prime \downarrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} = -\frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^z_m}^2{S_d^z}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(+|-\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m}\frac{1}{4}{J^t_m}^2 c^\dagger_{q \downarrow} c_{k^\prime \uparrow} S_d^+ \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{q \downarrow} = -\frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2S_d^+ \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{k^\prime\uparrow} }{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(-|+\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m}\frac{1}{4}{J^t_m}^2 c^\dagger_{q \uparrow} c_{k^\prime \downarrow} S_d^- \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2S_d^- \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{k^\prime\downarrow} }{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(z|+\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m} J^t_m c^\dagger_{q \uparrow} c_{k^\prime \uparrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^z_m} J^t_m \ket{m}\bra{m} S_d^z S_d^+ c^\dagger_{k \downarrow}c_{k^\prime\uparrow}}{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(-|z\)}
This is equal to the h.c. of the renormalization coming from \(z|+\), because \(-|z = \left(z|+\right)^\dagger \).

\paragraph{\(z|-\)}
\begin{equation}\begin{aligned}
	-\sum_{kk^\prime,m}\frac{1}{4}{J^t_m} J^z_m c^\dagger_{q \downarrow} c_{k^\prime \downarrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{q \downarrow} = \frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m} J^z_m \ket{m}\bra{m} S_d^z S_d^- c^\dagger_{k \uparrow}c_{k^\prime\downarrow}}{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
\end{aligned}\end{equation}

\paragraph{\(+|z\)}
This is equal to the h.c. of the renormalization coming from \(z|-\), because \(+|z = \left(z|-\right)^\dagger \).

The first four terms generate and renormalize a new three-particle term in the Hamiltonian, of the form \(J^{zz}{S_d^z}^2\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma}\). The third and fourth terms also renormalize the \(J^z_m\) coupling. The terms e through h renormalize \(J^t_m\). To compare with the spin-\(\frac{1}{2}\) Kondo URG, we redefine the \(\omega_{m\sigma} \to \omega + \frac{J}{2}\left(-\sigma m + \frac{1}{2}\right) \). We also use \(\sum_\sigma \hat n_{q\sigma}= n(D)\). The total renormalization from the first four terms is
\begin{equation}\begin{aligned}
	-\frac{1}{4}\sum_{kk^\prime\sigma}\frac{n(D)\left({J^z}^2 - {J^t}^2\right) {S_d^z}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma}}{\omega - D/2 + \frac{J}{4}} - \frac{1}{2}\sum_{kk^\prime}\frac{n(D){J_m^t}^2 {S_d^z} s^z_{kk^\prime}}{\omega - D/2 + \frac{J}{4}}
\end{aligned}\end{equation}
The renormalization from the last four terms is
\begin{equation}\begin{aligned}
	-\frac{1}{2}\sum_{kk^\prime, m}\frac{n(D)J^z_m J^t_m \left(S_d^+ s^-_{kk^\prime} + \text{h.c.}\right) m\ket{m}\bra{m}}{\omega - D/2 + \frac{J}{4}}
\end{aligned}\end{equation}
